### 2021-11-16 documents/sections/verbs.tex
'to say'

Our categorization of \qu{to say} as an intransitive verb is supported primarily by its person prefixes.
\kalina offers a minimal pair between transitive \obj{ka} \qu{to remove} and intransitive \obj{ka} \qu{to say}, \obj{sikai} \qu{I took it away} vs \obj{wɨkai} \qu{I said} \parencite[288, 45]{courtz2008carib}.\footnote{Interestingly, the \kalina causativized form \obj{kapo} \qu{to make say} does not have the regular \gl{1}>\gl{3} prefix \obj{s(i)-}, but irregular \obj{w(ɨ)-} \parencite[430]{courtz2008carib}.}
Similarly, \qu{to say} in Pekodian languages has a reflex of \gl{1}\gl{s} \rc{w-} \pcref{sec:pekodian}, and not \gl{1}>\gl{3} \obj{s-} (\bakairi) or \rc{ini-} (\PXin).
Additionally, languages which differentiate direct prefixes from \gl{s_a_} prefixes by the presence of \obj{i} \parencite[495]{meira2010origin} show no \obj{i} for this verb, see \exref{sayintr.aku-154} and  \textcites[294]{triomeira1999}[195]{wayanatavares2005}[288]{ikpengpacheco2001}[150]{alves2017arara}[168]{hoff1968carib}.
Finally, the \gl{s_a_} class marker \obj{w-} occurs on nominalizations in \kalina \exref{sayintr.kar-84}, and it is probably reflected as vowel length in the \trio \parencite[333]{triomeira1999} and \wayana \parencite[196]{wayanatavares2005} participles.

>>>>

Our categorization of \qu{to say} as an intransitive verb is supported primarily by its person prefixes.
\kalina offers a minimal pair between transitive \obj{ka} \qu{to remove} and intransitive \obj{ka} \qu{to say}, \obj{sikai} \qu{I took it away} vs \obj{wɨkai} \qu{I said} \parencite[288, 45]{courtz2008carib}.\footnote{Interestingly, the \kalina causativized form \obj{kapo} \qu{to make say} does not have the regular \gl{1}>\gl{3} prefix \obj{s(i)-}, but irregular \obj{w(ɨ)-} \parencite[430]{courtz2008carib}.}
Similarly, \qu{to say} in Pekodian languages has a reflex of \gl{1}\gl{s} \rc{w-} \pcref{sec:pekodian}, and not \gl{1}>\gl{3} \obj{s-} (\bakairi) or \rc{ini-} (\PXin).
Additionally, languages which differentiate direct prefixes from \gl{s_a_} prefixes by the presence of \obj{i} \parencite[495]{meira2010origin} show no \obj{i} for this verb, see \exref{sayintr.aku-154} as well as \textcites[294]{triomeira1999}[195]{wayanatavares2005}[288]{ikpengpacheco2001}[150]{alves2017arara}[168]{hoff1968carib} for the verb's inflection in individual languages.
Finally, the \gl{s_a_} class marker \obj{w-} occurs on nominalizations in \kalina \exref{sayintr.kar-84}, and it is probably reflected as vowel length in the \trio \parencite[333]{triomeira1999} and \wayana \parencite[196]{wayanatavares2005} participles.
